### 2018-05-09 submission/supplemental.Rmd
Add supplemental table legends and break up supp tables

---
title: ''
csl: mbio.csl
fontsize: 12pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=1.0in
bibliography: null
---

# Leveraging Existing 16S rRNA Gene Surveys to Identify Reproducible Biomarkers in Individuals with Colorectal Tumors

\vspace{10mm}

\begin{center}
Marc A Sze and Patrick D Schloss

\vspace{10mm}

Supplemental
\end{center}

```{r knitr_settings, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}

>>>>

---
title: ''
csl: mbio.csl
fontsize: 12pt
output:
  pdf_document:
    includes:
      in_header: header.tex
    keep_tex: yes
geometry: margin=0.75in
bibliography: null
---
\pagenumbering{gobble}
```{r knitr_settings, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE}
